Efficient pedigree recording for fast population genetics simulation

### 2018-01-10 forwards_paper.tex
Formatting fix

We coupled \simupop{} to \msprime{} using a Python class \texttt{RecombCollector} 1)
tracks time, and 2) collects and parses recombination information provided by
the \texttt{Recombinator} class of \simupop{}, adding them to a \tnodetable{} and
\tedgetable{} upon which simplification is performed every 1000 years (using
\texttt{msprime.sort\_tables()} and \texttt{msprime.simplify\_tables}).
The tables are initialized using the \texttt{TreeSequence} returned from
\texttt{msprime.simulate($2N$, Ne=$N$, recombination\_rate=$r/2$, length=$n$)}.
The \texttt{simuPOP.Population()} is initialized and tagged with individual IDs,
a mapping of these IDs to the \tnodetable IDs is passed to
an instance of \texttt{RecombCollector} and used internally to update the tables.
The \texttt{simuPOP.Population()} is then evolved.
Before mating: selected mutations are created (using
\texttt{simuPOP.SNPMutator}) and multiplicative selection occurs (using
\texttt{simuPOP.PyMlSelector}) only on the selected loci;
the internal time of the \texttt{RecombCollector} instance is updated.
During mating: male and female parents are drawn randomly, recombination data is
output by \simupop{} to the \texttt{RecombCollector} instance.
After mating: nothing happens 999/1000 years, every 1000 years the tables are
simplifed.

\texttt{RecombCollector} uses the Python class \texttt{ARGrecorder} internally
to add data to the tables and perform simplification.
This class contains the \tnodetable and \tedgetable and also the mapping from
(haploid) ids to ids in the tables.
It also provides methods (\texttt{add\_individual} and \texttt{add\_record})
to append data to the tables.
The only functions of
\texttt{RecombCollector} not delegated to this internal class are computing
haploid IDs from \simupop{}'s diploid IDs and parsing recomination data into
data suitible for use with use with \texttt{add\_individual} and
\texttt{add\_record}; these functions are used to stream data into the tables as
it is received by an instance of \texttt{RecombCollector}.

>>>>

We coupled \simupop{} to \msprime{} using a Python class \texttt{RecombCollector} 1)
tracks time, and 2) collects and parses recombination information provided by
the \texttt{Recombinator} class of \simupop{}, adding them to a \tnodetable{} and
\tedgetable{} upon which simplification is performed every 1000 years (using
\texttt{msprime.sort\_tables()} and \texttt{msprime.simplify\_tables}).
The tables are initialized using the \texttt{TreeSequence} returned from
\texttt{msprime.simulate($2N$, Ne=$N$, recombination\_rate=$r/2$, length=$n$)}.
The \texttt{simuPOP.Population()} is initialized and tagged with individual IDs,
a mapping of these IDs to the \tnodetable{} IDs is passed to
an instance of \texttt{RecombCollector} and used internally to update the tables.
The \texttt{simuPOP.Population()} is then evolved.
Before mating: selected mutations are created (using
\texttt{simuPOP.SNPMutator}) and multiplicative selection occurs (using
\texttt{simuPOP.PyMlSelector}) only on the selected loci;
the internal time of the \texttt{RecombCollector} instance is updated.
During mating: male and female parents are drawn randomly, recombination data is
output by \simupop{} to the \texttt{RecombCollector} instance.
After mating: nothing happens 999/1000 years, every 1000 years the tables are
simplifed.

\texttt{RecombCollector} uses the Python class \texttt{ARGrecorder} internally
to add data to the tables and perform simplification.
This class contains the \tnodetable{} and \tedgetable{} and also the mapping from
(haploid) ids to ids in the tables.
It also provides methods (\texttt{add\_individual} and \texttt{add\_record})
to append data to the tables.
The only functions of
\texttt{RecombCollector} not delegated to this internal class are computing
haploid IDs from \simupop{}'s diploid IDs and parsing recomination data into
data suitible for use with use with \texttt{add\_individual} and
\texttt{add\_record}; these functions are used to stream data into the tables as
it is received by an instance of \texttt{RecombCollector}.
